{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-03 documents/background.tex
Poisson boltzmann
delphi

We were inspired by Yang (gordon reuben following up)
bona fide clinically useful effect

@@

%3 MV/m * 1000 electronCharge * 1 angstrom / (boltzmannConstant * 310 K) = 1.12 kT
From a pessimistic energetic perspective,  !!! we know what the spring constant k should be !!!
, where 0.1 angstrom is derived from the lipid MD simulation. [that's not right!] Compare to ~5 $k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

@@

>>>>

\footnote{"nsPEFs"}

We were inspired to undertake this project by a set of publications by Yang et al, Hung et al, Sun et al.

bona fide clinically useful effect

Any technique that requires background subtraction (see).

We distinct regimes, which overlap in physical mechanisms (both involve the charge distribution and relaxation time) but which cite different bodies of literature. Vestiges

frequency-dependent inactivation

(gordon reuben following up)

@@

%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
From a pessimistic energetic perspective,  !!! we know what the spring constant k should be !!!
. We can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass.
, where 0.1 angstrom is derived from the lipid MD simulation. [that's not right!]

Compare to ~5 $k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

%(2*pi*(20 GHz))^2 * 100 MDa to N/m \approx 3000 N/m
% 1 nanonewton / (3000 N/m) = 3e-13 m

% (2*pi*(5 GHz))^2 * 60 MDa to N/m = 100 N/m
% 0.1 angstroms

% 1000 N/m = 0.01 Angstroms

@@

involving Schnelle
